
---
title: "Lab 5 Assignment"
author: "Emily Miller"
date: "2021-02-23"
output: github_document
---



# Load Packages -----------------------------------------------------------

```{r}
library(tidyverse)
```



# Data --------------------------------------------------------------------

```{r}
iris <- as_tibble(iris)
```



# Question 1 --------------------------------------------------------------

1. Rename each variable so that it is all lower-case and uses an underscore _ instead of a period . in the name (the recommended coding style in the tidyverse style guide). Print the resulting table.

```{r}
rename(
  iris,
  sepal_length = Sepal.Length,
  sepal_width = Sepal.Width,
  petal_length = Petal.Length,
  petal_width = Petal.Width
)
```



# Question 2 --------------------------------------------------------------

2. Convert the four numerical variables from cm to mm by multiplying by 10. Print the resulting table.

```{r}
iris2 <- mutate(
  iris,
  Sepal.Length = Sepal.Length * 10,
  Sepal.Width = Sepal.Width * 10,
  Petal.Length = Petal.Length * 10,
  Petal.Width = Petal.Width * 10
)
```



# Question 3 --------------------------------------------------------------

3. Calculate sepal area and petal area (area is equal to length multiplied by width). Print a table with only the variables sepal area, petal area, and species.


```{r}
mutate(iris,
       sepal_area = Sepal.Length * Sepal.Width,
       petal_area = Petal.Length * Petal.Width)
```


# Question 4 --------------------------------------------------------------

4. Calculate the following statistics for the entire dataset from the sepal length variable and print the resulting table:

  a. sample size
  b. maximum value
  c. minimum value
  d. range
  e. median
  f. first quartile (q1)
third quartile (q2)
inter-quartile range (iqr)


```{r}
summarise(iris, sample_size=n())

summarize(iris, max_Sepal.Length=max(Sepal.Length))
summarize(iris, min_Sepal.Length=min(Sepal.Length))
summarize(iris, range_Sepal.Length=range(Sepal.Length))
summarize(iris, median_Sepal.Length=median(Sepal.Length))
summarize(iris, q1=quantile(Sepal.Length, probs=0.25))
summarize(iris, q2=quantile(Sepal.Length, probs=0.75))
summarize(iris, IQR_Sepal.Length=IQR(Sepal.Length))
```



# Question 5 --------------------------------------------------------------

5. Calculate the following statistics for each species from the petal width variable and print the resulting table:

  a. sample size
  b. mean
  c. standard deviation
  d. variance
  e. standard error of the mean
  f. approximate 95% confidence interval
  
  
```{r}
speciesgrouped <- group_by(iris, Species)

PetalWidth <- summarize(
  speciesgrouped,
  sample_size = n(),
  mean_Petal.Width = mean(Petal.Width),
  sd_Petal.Width = sd(Petal.Width),
  var_Petal.Width = var(Petal.Width),
  sem = sd(Petal.Width) / (sqrt(n())),
  ci_upper_limit = mean_Petal.Width + 1.96 * sem,
  ci_lower_limit = mean_Petal.Width - 1.96 * sem
)
```

# Question 6 and 7--------------------------------------------------------------

6 and 7. Visualize the relationship between petal width and species using a strip plot. Then add the mean and 95% confidence interval for each species.




# Question 8 --------------------------------------------------------------

8. Visualize the relationship between petal length, petal width, and species using a scatterplot. Map the two numerical variables to the x and y axes and map species to the color and shape aesthetics.

```{r}
ggplot(data= iris) +
  geom_point(mapping=aes(x=Petal.Length, y =Petal.Width, color=Species),
  )
```


# Session Info ------------------------------------------------------------

```{r session-info}
sessioninfo::session_info()
```