
---
title: "Lab 5 Assignment"
author: "Emily Miller"
date: "2021-02-23"
output: github_document
---

Welcome to my lab 5 assignment

# Load Packages 

```{r message=FALSE}
library(tidyverse)
```



# Data

```{r}
iris <- as_tibble(iris)
```



# Question 1

1. Rename each variable so that it is all lower-case and uses an underscore _ instead of a period . in the name (the recommended coding style in the tidyverse style guide). Print the resulting table.

```{r}
rename(
  iris,
  sepal_length = Sepal.Length,
  sepal_width = Sepal.Width,
  petal_length = Petal.Length,
  petal_width = Petal.Width
)
```



# Question 2

2. Convert the four numerical variables from cm to mm by multiplying by 10. Print the resulting table.

```{r}
iris2 <- mutate(
  iris,
  Sepal.Length = Sepal.Length * 10,
  Sepal.Width = Sepal.Width * 10,
  Petal.Length = Petal.Length * 10,
  Petal.Width = Petal.Width * 10
)
```



# Question 3

3. Calculate sepal area and petal area (area is equal to length multiplied by width). Print a table with only the variables sepal area, petal area, and species.


```{r}

iris2 <- mutate(iris,
       sepal_area = Sepal.Length * Sepal.Width,
       petal_area = Petal.Length * Petal.Width)

select(iris2, sepal_area, petal_area, Species)
```


# Question 4

4. Calculate the following statistics for the entire dataset from the sepal length variable and print the resulting table:

  a. sample size
  b. maximum value
  c. minimum value
  d. range
  e. median
  f. first quartile (q1)
  g. third quartile (q2)
  h. inter-quartile range (iqr)


```{r}
summarise(
  iris,
  sample_size = n(),
  max= max(Sepal.Length),
  min= min(Sepal.Length),
  range= max-min,
  median= median(Sepal.Length),
  q1 = quantile(Sepal.Length, probs = 0.25),
  q2 = quantile(Sepal.Length, probs = 0.75),
  iqr= IQR(Sepal.Length)
)
```



# Question 5

5. Calculate the following statistics for each species from the petal width variable and print the resulting table:

  a. sample size
  b. mean
  c. standard deviation
  d. variance
  e. standard error of the mean
  f. approximate 95% confidence interval
  
  
```{r}
speciesgrouped <- group_by(iris, Species)

PetalWidth <- summarize(
  speciesgrouped,
  sample_size = n(),
  mean_Petal.Width = mean(Petal.Width),
  sd_Petal.Width = sd(Petal.Width),
  var_Petal.Width = var(Petal.Width),
  sem = sd(Petal.Width) / (sqrt(n())),
  ci_upper_limit = mean_Petal.Width + 1.96 * sem,
  ci_lower_limit = mean_Petal.Width - 1.96 * sem
)
PetalWidth
```

# Question 6 and 7

6 and 7. Visualize the relationship between petal width and species using a strip plot. Then add the mean and 95% confidence interval for each species.

```{r}
ggplot(data=iris)+
  geom_jitter(mapping=aes(x=Species, y=Petal.Width))



ggplot(data = iris) +
  geom_jitter(mapping = aes(y = Petal.Width, x = Species)) +
  geom_crossbar(
    data = PetalWidth,
    mapping = aes(
      x = Species,
      y = mean_Petal.Width,
      ymax = ci_upper_limit,
      ymin = ci_lower_limit
    ),
    color = "blue"
  )
```



# Question 8

8. Visualize the relationship between petal length, petal width, and species using a scatterplot. Map the two numerical variables to the x and y axes and map species to the color and shape aesthetics.

```{r}
ggplot(data = iris) +
  geom_point(mapping = aes(
    x = Petal.Length,
    y = Petal.Width,
    color = Species,
    shape = Species
  ))
```


# Session Info 

```{r session-info}
sessioninfo::session_info()
```